material and methods

### 2018-03-27 man/ms_1_material_methods.Rmd
mas update

In addition, the forest history of San Juan and Cáñar sites was inferred from a detailed analysis of historical land-use changes. For this purpose, an exhaustive review of historical documents was done to compile information about socio-economical activities affecting forest: land-uses, forest managment actions, mining, wildfires, etc. Several documentary sources were reviewed: historical documents and maps [*e.g.* @Catastro1752; @Ministerio1943; @Titos1990]; detailed mining reports [*e.g.* @Maestre1858]; official information about recent wildfires events (Regional Ministry for the Environment of the Government of Andalusia) and forest management practices [@Bonet2016obsnev_forest]; livestock farming [*e.g.* @MorenoLlorca2014] and other studies reviewing the socioeconomic dynamics of forest of Sierra Nevada at different scales [@Bonet2014_conama; @JimenezOlivencia2015; @MorenoLlorca2016].

>>>>

In addition, the forest history of San Juan and Cáñar sites was inferred from a detailed analysis of historical land-use changes. For this purpose, an exhaustive review of historical documents was done to compile information about socio-economical activities affecting forest: land-uses, forest managment actions, mining, wildfires, etc. Several documentary sources were reviewed: historical documents and maps [*e.g.* @Catastro1752; @Ministerio1943; @Titos1990]; detailed mining reports [*e.g.* @Maestre1858]; official information about recent wildfires events (Regional Ministry for the Environment of the Government of Andalusia) and forest management practices [@Bonet2016obsnev_forest]; livestock farming [*e.g.* @MorenoLlorca2014]; and other studies reviewing the socioeconomic dynamics of forest of Sierra Nevada at different scales [@Bonet2014_conama; @JimenezOlivencia2015; @MorenoLlorca2016].
